Increased perceptions of autonomy through choice fail to enhance motor skill retention

### 2021-05-20 docs/preprint/preprint.Rmd
init

authornote: |
  \addORCIDlink{Laura St. Germain}{0000-0002-5513-4183}

  \addORCIDlink{Keith R. Lohse}{0000-0002-7643-3887}

  \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}

@@

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

csl               : "../apa-single-spaced.csl"
documentclass     : "apa7"
classoption       : "man" # man for manuscript & jou for journal
output            : papaja::apa6_pdf
header-includes   :
  - \pagewiselinenumbers
  - \raggedbottom
  - \leftheader{\textbf{THIS PREPRINT HAS BEEN SUBMITTED FOR PEER-REVIEW}}
  - \rightheader{\textbf{THIS PREPRINT HAS BEEN SUBMITTED FOR PEER-REVIEW}}
  #- \hypersetup{draft} # comment out after but right now will prevent error message about some link spanning multiple pages
---

@@

apa_table(table_1, font_size = "scriptsize", col.names = c(" ", "Acquisition instructions"), booktabs = TRUE, span_text_columns = TRUE, caption = "Group specific instructions detailing the observation schedule that would be experienced during Acquisition.")

@@

```{r fig1, echo = FALSE, fig.cap = "(ref:fig1-caption)", fig.align = "center", out.height = "55%"}
knitr::include_graphics("../../figs/fig1.pdf")
```

@@

apa_table(table_2, font_size = "scriptsize", col.names = c(" ", "Block 1", "Block 2", "Block 3", "Block 4", "Block 5"), booktabs = TRUE, span_text_columns = TRUE, caption = "The mean frequencies for each acquisition block of requesting to watch the video demonstration and choosing the regular viewing speed.", placement = "t")

@@

```{r fig2, echo = FALSE, fig.cap = "(ref:fig2-caption)", fig.align = "center", out.height = "75%"}
knitr::include_graphics("../../figs/fig2.pdf")

@@

>>>>

authornote: |
  \addORCIDlink{Laura St. Germain}{0000-0002-5513-4183}; \addORCIDlink{Keith R. Lohse}{0000-0002-7643-3887}; \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}

@@

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

csl               : "../apa-single-spaced.csl"
documentclass     : "apa7"
classoption       : "jou" # man for manuscript & jou for journal
output            : papaja::apa6_pdf
header-includes   :
  # - \pagewiselinenumbers
  - \raggedbottom
  - \leftheader{\textbf{THIS PREPRINT HAS BEEN SUBMITTED FOR PEER-REVIEW}}
  - \rightheader{\textbf{THIS PREPRINT HAS BEEN SUBMITTED FOR PEER-REVIEW}}
  #- \hypersetup{draft} # comment out after but right now will prevent error message about some link spanning multiple pages
---

@@

apa_table(table_1, col.names = c(" ", "Acquisition instructions"), booktabs = TRUE, span_text_columns = TRUE, caption = "Group specific instructions detailing the observation schedule that would be experienced during Acquisition.")

@@

```{r fig1, echo = FALSE, fig.cap = "(ref:fig1-caption)", out.width = "100%", out.height = "100%", fig.align = "center", fig.env = "figure*"}
knitr::include_graphics("../../figs/fig1.pdf")
```

apa_table(table_2, col.names = c(" ", "Block 1", "Block 2", "Block 3", "Block 4", "Block 5"), booktabs = TRUE, span_text_columns = TRUE, caption = "The mean frequencies for each acquisition block of requesting to watch the video demonstration and choosing the regular viewing speed.", placement = "t")

@@

@@

@@

```{r fig2, echo = FALSE, fig.cap = "(ref:fig2-caption)", out.width = "85%", out.height = "85%", fig.align = "center", fig.env = "figure*"}
knitr::include_graphics("../../figs/fig2.pdf")
